Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-09 sections/srfm.tex
Added on ref

The best resolution (approximately 2\,nm) obtained by STED microscopy has
been recorded on samples containing fluorescent color centers in diamond
crystal \cite{Wildanger2012}. Note that, by applying a depletion beam of a
different shape, STED microscopy allows to improve the resolution along the
optical axis \cite{Wildanger2009}. A large number of reviews articles exist
which summarize the use of STED (or in general, RESOLFT) microscopy in different
fields in the life sciences, much too much to be listed here. We would like to
refer the reader to exhaustive reviews, which, besides
reviewing various applications, detail technical aspects of STED microscopy
\cite{Turkowyd2016,Blom2017} as well as to a review which contains some
anecdotal sections on how STED was developed \cite{Sahl2019}.

>>>>

The best resolution (approximately 2\,nm) obtained by STED microscopy has
been recorded on samples containing fluorescent color centers in diamond
crystal \cite{Wildanger2012}. Note that, by applying a depletion beam of a
different shape, STED microscopy allows to improve the resolution along the
optical axis \cite{Harke2008, Wildanger2009}. A large number of reviews articles exist
which summarize the use of STED (or in general, RESOLFT) microscopy in different
fields in the life sciences, much too much to be listed here. We would like to
refer the reader to exhaustive reviews, which, besides
reviewing various applications, detail technical aspects of STED microscopy
\cite{Turkowyd2016,Blom2017} as well as to a review which contains some
anecdotal sections on how STED was developed \cite{Sahl2019}.
